---
title: "Jon Lab5 Individual"
author: "Jon Guay"
date: "February 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
milk <- read.csv('state_milk_production.csv')
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
```


```{r}
milk_1999 <- milk %>%
  filter(year == 1999)
ggplot(data = milk_1999) +
geom_density(mapping = aes(x = milk_million)) +
  ggtitle('Distribution of Milk for my Birth Year: 1999')
```

```{r}
Part2 <- milk %>%
  filter(year == 1999) %>%
  summarize(average = mean(milk_million),
            middle = median(milk_million), max(milk_million),min(milk_million))
Part2
```

```{r}
Jonteampart <- milk %>%
  filter(state %in% c('Wisconsin', 'Florida', 'Colorado', 'Texas', 'California')) %>%
           select(state,year,milk_million)
ggplot(data = Jonteampart, aes(x = year, y = milk_million, color = state)) +
  geom_point() + 
  ggtitle('Pounds of milk over time by state') +
  xlab('Year') +
  ylab('Milk Produced (Million lb)') +
  geom_smooth(data = averageplot, mapping = aes(x = year, y = avg))
```

```{r}
averageplot <- milk %>%
  filter(state %in% c('Wisconsin', 'Florida', 'Colorado', 'Texas', 'California')) %>%
           select(state,year,milk_million) %>%
  group_by(year,state) %>%
  summarize(avg = mean(milk_million))
  
```

This plot lets us know that Wisconsin was the largest milk producer  of these 5 states in 1970, but then was overtaken by california in about 1995.  The other 3 states stayed right around their normal production, with colorado and Texas slightly increasing, and Florida experiencing a slight decrease in overall production.

FOR LUCAS:
Lucas, paste this expression into every chunk to hide all error and code messages when you knit. {r, echo = FALSE, results = 'hide', message = FALSE}