---
title: "Pink_Lemonade_LA5"
author: "Pink Lemonade- Lucas Brack, Jon Guay, Max Ward, Harold Chang"
date: "February 15, 2019"
output: html_document
---
#Team Plots
```{r setup, include=FALSE, results='hide', message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
milk <- read.csv('state_milk_production.csv')
milk <- milk %>%
  mutate(milk_million = milk_produced/1000000)
```
##Average Milk Production for 5 States Since 1970
```{r, echo = FALSE, message = FALSE}

averageplot <- milk %>%

  filter(state %in% c('Wisconsin', 'Florida', 'Colorado', 'Texas', 'California')) %>%

           select(state,year,milk_million) %>%

  group_by(year,state) %>%

  summarize(avg = mean(milk_million))


```

```{r, echo = FALSE, message = FALSE}

Jonteampart <- milk %>%

  filter(state %in% c('Wisconsin', 'Florida', 'Colorado', 'Texas', 'California')) %>%

           select(state,year,milk_million)

ggplot(data = Jonteampart, aes(x = year, y = milk_million, color = state)) +

  geom_point() + 

  ggtitle('Pounds of milk over time by state') +

  xlab('Year') +

  ylab('Milk Produced (Million lb)') +

  geom_smooth(data = averageplot, mapping = aes(x = year, y = avg))

```


This plot lets us know that Wisconsin was the largest milk producer  of these 5 states in 1970, but then was overtaken by california in about 1995.  The other 3 states stayed right around their normal production, with colorado and Texas slightly increasing, and Florida experiencing a slight decrease in overall production.

##Year With the Most Milk Production

```{r, echo = FALSE, message = FALSE}

yearmost <-milk%>%

  group_by(year)%>%

  summarize(totalmilk = sum(milk_million))%>%

  arrange(desc(totalmilk))

yearmost

```

##Year With the Least Milk Production 

```{r, echo = FALSE, message = FALSE}

group_by(milk,year)%>%

  summarise(totalmilk = sum(milk_million))%>%

  arrange((totalmilk))


```

##Most Milk Produced in 2017

```{r, echo = FALSE, message = FALSE}

MaxTeam <- milk %>%

  filter(year == 2017)%>%

  group_by(state)%>%

  arrange(desc(milk_million))

MaxTeam

```

As we can see from the data in 2017 the top five states in milk production were Califorina, Wisconsin, New York, Idaho and Texas.

##Least Milk Produced 2017
```{r, echo = FALSE, message = FALSE}

MaxTeam <- milk %>%

  filter(year == 2017)%>%

  group_by(state)%>%

  arrange(desc(-milk_million))

MaxTeam

```

As we can see for this data is that in 2017 the lowest five states in milk production were Alaska, Rhode Island, Hawaii, Arkansas and Alabama.

#Individual Plots

###Jon Guay
```{r, echo = FALSE, message = FALSE}

milk_1999 <- milk %>%

  filter(year == 1999)

ggplot(data = milk_1999) +

geom_density(mapping = aes(x = milk_million)) +

  ggtitle('Distribution of Milk for my Birth Year: 1999')

```

```{r, echo = FALSE, message = FALSE}

Part2 <- milk %>%

  filter(year == 1999) %>%

  summarize(average = mean(milk_million),

            middle = median(milk_million), max(milk_million),min(milk_million))

Part2

```

###Harold Chang
```{r, echo = FALSE, message = FALSE}

milk1996 <- milk %>%

  filter(year == 1996)

ggplot(data = milk1996, aes(x = milk_million)) +

  geom_density() + 

  ggtitle('Distribution estimate of milk produced in 1996 by state')

```

```{r, echo = FALSE, message = FALSE}

statemilk <- milk1996 %>%

group_by(state)%>%

summarise(avgproduction = mean(milk_million, na.rm = TRUE))

statemilk

```

```{r, echo = FALSE, message = FALSE}

statemilk2 <- milk1996 %>%

group_by(state)%>%

summarise(medianproduction = median(milk_million, na.rm = TRUE))

statemilk2

```

```{r, echo = FALSE, message = FALSE}

most <-milk1996 %>%

  group_by(state)%>%

  summarise(max=max(milk_million))

  #arrange((milk_million))



#library(dplyr)

most[with(most, order(-max)), ]

```

```{r, echo = FALSE, message = FALSE}

least <-milk1996%>%

  group_by(state)%>%

  summarise(min=min(milk_million))

  #arrange((milk_million))

  

least


#library(dplyr)

least[with(least, order(min)), ] 

```

###Max Ward
```{r, echo = FALSE, message = FALSE}

milk1998 <- milk %>%

  filter(year == 1998)

ggplot(data = milk1998, aes(x = milk_million)) +

  geom_density() + 

  ggtitle('Distribution estimate of milk produced in 1998 by state')

```

```{r, echo = FALSE, message = FALSE}

Individual_Part2 <- milk %>%

  filter(year == 1998) %>%

  summarize(average = mean(milk_million),middle = median(milk_million),

            max(milk_million),min(milk_million))
Individual_Part2

```

```{r, echo = FALSE, message = FALSE}

statemilk <- milk1998 %>%

group_by(state)%>%

summarise(medianproduction = median(milk_million, na.rm = TRUE))

statemilk

```

```{r, echo = FALSE, message = FALSE}

statemilk2 <- milk1998 %>%

group_by(state)%>%

summarise(avgproduction = mean(milk_million, na.rm = TRUE))

statemilk2

```

###Lucas Brack
```{r, echo = FALSE, message = FALSE}
birthMilk <- milk %>%
filter(year %in% c('2000'))
```

```{r, echo = FALSE, message = FALSE}
ggplot(data= birthMilk, aes(x = milk_million, fill=state)) +
  geom_histogram(bins = 30) +
  xlim(0, 33000)+
  ylim(0, 14)+
  labs(title="Histogram of milk produced in 2000 by state",x="Millions of lbs of Milk Produced" )
```

```{r, echo = FALSE, message = FALSE}
birthSum <- birthMilk %>%
  summarize(mean(milk_million), median(milk_million), max(milk_million), min(milk_million))
birthSum
```
